%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://timweri.me/}{\Large Thanh Nguyen}} & Email : \href{mailto:thanh@timweri.me}{thanh@timweri.me}\\
  % \href{http://timweri.me/}{http://www.timweri.me} & \\
  {Software Engineer} & \\
\end{tabular*}

% \bigskip
% \textbf{Skills}
% \vspace{-5pt}
% \begin{itemize}
%   \item Proficient: C++, C, Python, AWS\vspace{-5pt}
%   \item Familiar: NodeJS, Golang
% \end{itemize}
% \vspace{-15pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON, Canada}
      {Bachelor of Computer Science (Dean's Honour); GPA: 3.9}{Sep 2017 -- Apr 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Capital One}{Toronto, ON, Canada}
      {Software Engineer}{Sep 2021 - Dec 2021, Jun 2022 - Current}
      \resumeItemListStart
        \resumeItem{Quick Check}
          {Quick Check is an \textbf{AWS} Serverless application, built with \textbf{Golang} and \textbf{React}, to assess credit card applicants' eligibility using soft credit checks.
          Implemented new API specifications and clearer HTTP errors to minimize customers' frustration when Quick Check fails. }
        \resumeItem{One Email}
          {Designed and built the initial version of One Email.
          One Email is an \textbf{AWS} Serverless application to send automated emails to customers, triggered by \textbf{Kafka} streams.
          One Email allows teams to replace near-identical email infrastructures with one unified email infrastructure through pure YAML configurations. }
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Huawei}{Markham, ON, Canada}
      {Compiler Software Engineer Co-op}{May 2021 - Aug 2021}
      \resumeItemListStart
        \resumeItem{GPU Compiler Optimization}
          {Optimized \textbf{LLVM}-based GPU Compiler written in \textbf{C++}: Implemented stack spill to different types of memories to make use of faster types of memories when possible. 
          Worked with \textbf{LLVM} intermediate representations in the Analysis and Transform phases.}
      \resumeItemListEnd

    \resumeSubheading
      {Wayfair}{Boston, MA, USA}
      {Software Engineer Co-op}{Jan 2020 - May 2020}
      \resumeItemListStart
        \resumeItem{CI/CD Optimization}
          {Designed and implemented a CI/CD solution to improve the experience of configuring CI/CD pipelines for different projects in the monolith. Onboarded 15+ teams.
          Reduced redundant build jobs and reduced total build jobs by 33\%.
          Enabled efficient static analyses of projects. }
        \resumeItem{GCP Autoscale}
        {Configured \textbf{GCP} compute clusters using \textbf{Terraform} and custom metric services to autoscale according to CI/CD workload to save cost and to reduce build wait time during peak hours.}
      \resumeItemListEnd

    \resumeSubheading
      {BlackBerry}{Mississauga, ON, Canada}
      {Student Software Developer}{May 2019 - Aug 2019}
      \resumeItemListStart
        \resumeItem{SDK Development}
          {Implemented a new feature in the SDK to allow developers to scan APKs for threat using a machine learning model.
          Designed and built a proof-of-concept \textbf{Android} application to demo the APK scanning feature. }
        \resumeItem{Development Endpoint}
          {Designed and implemented an API endpoint using \textbf{ExpressJS} to deploy the APK machine learning model for development environments. 
          This facilitated teams to iterate faster and avoid using restrictive production endpoints for development. }
      \resumeItemListEnd

    \resumeSubheading
      {Trend Micro}{Ottawa, ON, Canada}
      {Software Engineer Co-op}{Sep 2020 - Dec 2020}
      \resumeItemListStart
        \resumeItem{Single Sign-On}
          { Implemented a new API specification to manage AWS Cognito JWT tokens. The API allows clients to reuse one token across multiple applications, avoiding repeated sign-in. }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Solidity (https://github.com/ethereum/solidity)}
    {Optimized the official compiler for \textbf{Solidity}, the popular \textbf{Ethereum} smart contract programming language.
      Improved gas cost by optimizing the generation of \textbf{Yul} intermediate respresentation.
      Improved error reporting and fixed compiler crashes. }
    \resumeSubItem{Microkernel}
      {A multi-threaded microkernel for a single core ARM chip.
      The microkernel supports syscalls, message passing, await event and such without any external libraries. }
    \resumeSubItem{Joos Compiler}
      {A compiler for simplified Java, built from scratch.
      The compiler supports inheritance, function overloading and external module import. }
    \resumeSubItem{Volumetric Reconstruction}
      {Implemented a blend of two space-carving algorithms to generate an interactive 3D cloud-point object from 2D images of an object from various angles. }
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
